Benchmarking neuromorphic systems with Nengo

### 2015-07-30 paper/paper.tex
Add cover letter
And a few other changes from the submission process.

  \tiny
  % 5--8 keywords
  \keyFont{ \section{Keywords:} Nengo, benchmarking, neuromorphic hardware }
\end{abstract}

@@

All of the software packages discussed in this paper
are available online,
except for the Brainstorm backend,
which has not yet been publicly released
(see Table~\ref{tab:02}).
All of the benchmarks presented here,
as well as the scripts used to generate
the presented figures,
are available at
\url{https://github.com/ctn-archive/bekolay-fnme2015}.
The results of running the benchmarks
are not included in the repository;
however, they can be downloaded separately at
\url{http://dx.doi.org/10.6084/m9.figshare.1496569}
to replicate the figures in this paper.

>>>>

  \tiny
  % 5--8 keywords
  \keyFont{ \section{Keywords:} Nengo, benchmarking, neuromorphic hardware,
    large-scale neural networks, spiking neural networks}
\end{abstract}

@@

All of the software packages discussed in this paper
are available online,
except for the Brainstorm backend,
which has not yet been publicly released
(see Table~\ref{Tab:02}).
All of the benchmarks presented here,
as well as the scripts used to generate
the presented figures,
are available at
\url{https://github.com/ctn-archive/bekolay-fnme2015}.
The results of running the benchmarks
are not included in the repository;
however, they can be downloaded separately at
\url{http://dx.doi.org/10.6084/m9.figshare.1496569}
to replicate the figures in this paper.
